---
title: "MA615_Assignment2_Exercise"
author: "Sky Liu"
date: "9/24/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gridExtra)
library(grid)
pacman::p_load(ggplot2, knitr,shiny,tidyverse,car,nycflights13)
```



#3.5.1(2) What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?

```{r}
ggplot(data = mpg) +   
  geom_point(mapping = aes(x = drv, y = cyl)) +
  facet_grid(drv ~ cyl)
```


The empty cells imply that the data set has no values within this row range and combination. In this plot, it shows there is four wheel driver with 5 cylinder is missing nor rear wheel driver with 4 or 5 cylinder.

#3.5.1(3)  What plots does the following code make? What does . do?
```{r}

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

```


The dot is used to indicate there should be no faceting on this dimension.


#3.6.1(6) Recreate the R code necessary to generate the following graphs.
```{r}
p1 <- ggplot(data = mpg, mapping = aes(x=displ,y=hwy)) +
  geom_smooth(se = FALSE ,method = 'loess')+ 
  geom_point()

p2 <- ggplot(data = mpg, mapping = aes(x=displ,y=hwy,group=drv)) +
  geom_smooth(se = FALSE)+ 
  geom_point()

p3 <- ggplot(data = mpg, mapping = aes(x=displ,y=hwy,group=drv)) +
  geom_smooth(se = FALSE,aes(colour=drv))+ 
  geom_point(aes(colour=drv))

p4 <- ggplot(data = mpg, mapping = aes(x=displ,y=hwy)) +
  geom_smooth(se = FALSE)+ 
  geom_point(aes(colour=drv))

p5 <- ggplot(data = mpg, mapping = aes(x=displ,y=hwy,group=drv)) +
  geom_smooth(se = FALSE,aes(linetype=drv))+ 
  geom_point(aes(colour=drv))

p6 <- ggplot(data = mpg, mapping = aes(x=displ,y=hwy)) +
  geom_point(aes(colour=drv))
grid.arrange(p1,p2,p3,p4,p5,p6,nrow=3,ncol=2)
```


#5.2.4(1) Find all flights that
##1. Had an arrival delay of two or more hours
```{r}
flights1 <- filter(flights, arr_delay>=120)
```

##2. Flew to Houston (IAH or HOU)
```{r}
flights2 <- filter(flights, dest %in% c('IAH', 'HOU'))
```

##3. Were operated by United, American, or Delta
```{r}
flights3 <- filter(flights, carrier %in% c('UA', 'AA', 'DL'))
```


##4. Departed in summer (July, August, and September)
```{r}
flights4 <- filter(flights, month %in% c(7, 8, 9))
```

##5. Arrived more than two hours late, but didn’t leave late
```{r}
flights5 <- filter(flights, arr_delay > 60*2 & dep_delay <= 0)
```

##6. Were delayed by at least an hour, but made up over 30 minutes in flight
```{r}
flights6 <- filter(flights, dep_delay >= 60 & dep_delay-arr_delay > 30)
```


##7. Departed between midnight and 6am (inclusive)
```{r}
flights7_1 <- filter(flights, dep_time >= 2400 & dep_time <= 600)
```


#5.2.4(2) Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?

##7. Departed between midnight and 6am (inclusive)
```{r}
flights7_2 <- filter(flights, !between(dep_time, 601, 2359))
```


#5.2.4(3) How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
sum(is.na(flights$dep_time))
map(flights, ~ sum(is.na(.x)))
```

Cancelled flights maybe?

#5.2.4(4) Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)

NA ^ 0 is not missing because anything to the power of 0 is 1.

NA | TRUE is not missing because the boolean value returned by this expression is TRUE.

FALSE & NA is not missing because because the boolean value returned by this expression is FALSE.

The general rule is that as long as there is a logical judgement of the expression, the result should not be NA.